{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-10 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

    Definition \ref{def:pg-opt} is the definition of the proximal gradient operator, which is equivalent to the gradient descent operator when the non-smooth part of the objective is the zero function. 
    To show the convergence of a stochastic case of the Nesterov's accelerated proximal gradient, we prepared Lemma \ref{thm:jesen} and, \ref{thm:pg-ineq}. 
    They are crucial in the derivation of the convergence. 
    The derivation for the convergence rate of a stochastic accelerated variant of Nesterov's accelerated  proximal gradient method is in the next section. 

@@

        \begin{definition}[semi relative smoothness and Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}

@@

        \begin{theorem}[affine composition with strong convexity and smoothness]\label{thm:smooth-aff-sq-scnvs-fxn}

@@

            Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary. 
            Let $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$, then the function $h$ satisfies: 
                (\forall x \in \RR^m)(\forall y \in \RR^m)\; \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
                \le D_h(x, y) \le \frac{L}{2}\Vert Ax - Ay\Vert^2. 
            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$. 

@@

                &\le \frac{L}{2} \Vert Ax - Ay\Vert^2. 

@@

        The following definition defines the concept of relative smoothness. 
        We build the proximal gradient inequality for the class of Semi-SCNVX functions. 

@@

            The following assumptions are ordered from weakest to strongest. 
            All of them are some of smooth with a non-smooth function. 
            \begin{assumption}[affine S-CNVX composition plus non-smooth]\label{ass:snorm-smth-p-nsmth}
                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:smooth-aff-sq-scnvs-fxn} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$. 

@@

@@

                    F(z) - F(x^+) 

@@

                At (b), we used the fact that $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} so, it has for all $x, z \in \RR^m$, $D_f(z, x) \ge \frac{\mu}{2}\Vert z - x\Vert^2$. 
                Since $\Pi = \Pi_{\ker A}$ to be the projection onto the kernel of matrix $A$, $z - x$ can be written as $\Pi(z - x) + (z - x) - \Pi(z - x)$ and so: 
                    & \Pi(z - x) \perp (z - x) - \Pi(z - x)
                    \implies & 
                    \Vert z - x\Vert^2 = \Vert \Pi(z - x) \Vert^2 + \Vert (z - x) - \Pi(z - x)\Vert^2
                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value, then it has: 
                    \Vert A(x - z)\Vert^2 &= \Vert A( \Pi(z - x)  + (z - x) - \Pi(z - x))\Vert^2
                    &= \Vert A((z - x) - \Pi(z - x))\Vert^2
                    &\ge \sigma_{\min}(A)^2\Vert (z - x) - \Pi(z - x)\Vert^2.
                Using two of the above results to keep simplifying the inequality, it yields: 
                    F(z) - F(x^+)

@@

                    F(z) - F(x^+)

@@

                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (z - x) - \Pi(z - x) \Vert^2

@@

                    F(z) - F(x^+)
                Last equality we used the fact that $\Pi$ is an linear operator as well. 

@@

                \todoinline{NOT YET FINISHED}

@@

                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2. 
                Let $\Pi = \Pi_{\ker A}$ be the projection onto the kernel of $A$, then it has: 
                    \Vert Ax - Ay\Vert^2 &= \Vert A\Pi(x - y) + (I - \Pi)(x - y) \Vert^2
                    \Vert A\Pi(x - y) \Vert^2 + \Vert A(I - \Pi)(x - y) \Vert^2
                    &\ge 0 + \sigma_{\min}(A)^2\Vert (I - \Pi)(x - y) \Vert^2
                Therefore, it gives the weaker inequality: 

@@

\section{Stochastic accelerated proximal gradient}
    In this section, we define the Stochastic accelerated Nesterov's Acceleration algorithm and, progressively build up the results to the one step convergence of the algorithm. 
    The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{n\times m}$ matrices. 
        Suppose $F:\RR^n \rightarrow \overline \RR:= (1/n)\left(\sum_{i = 1}^{n} f_i(x) + g_i(x)\right)$. 
        Assume
            \item 

@@

    \begin{assumption}[sum of many]\label{ass:sum-of-many}
        Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$.
        Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 

@@

        Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
    This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
    It still appears in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$. 
    In practice, each of the strong convexity constant $\mu^{(i)}$ may not be easily accessible. 
    And we further note that if $\mu > 0$ strongly convex, then there exists at least one $\mu^{(i)} \ge 0$. 

@@

    The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
    The following assumption state the interpolation hypothesis in our context. 
    \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
        Suppose that $F := (1/n)\sum_{i = 1}^{n} F_i$ satisfying Assumption \ref{ass:sum-of-many}. 
        In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
        Consequently, each of the $F_i$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth-x} with $X_i$ being the set of minimizers and, under interpolation hypothesis this equates to non-empty intersections between all $X_i$, i.e: $\bigcap_{i = 1}^n X_i \neq \emptyset$. 

@@

    \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
        Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
        Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
        Let $\tilde \mu \ge 0$ be a constant that is fixed.
        The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
    The following lemma state the relationships of the iterates generated by SNAPG-V2. 
    They are needed for the convergence proof. 
    \begin{lemma}[properties of the iterates \textcolor{red}{NEW}]\label{lemma:snapg2-itrs-props}
        Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 

@@

            \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 

@@

                    \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                    + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
            \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$

@@

        From Definition \ref{def:snapg-v2}, it has

@@

                1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}

@@

                \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}

@@

            = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 

@@

            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
                v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}

@@

            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
            + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}

@@

                \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)

@@

            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}

@@

                \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}

@@

            \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 

@@

            - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 

@@

            - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})

@@

                \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}

@@

            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})

@@

                \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}

@@

            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
            + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
            + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).

@@

    \end{proof}
    % --------------------------------------------------------------------------------------------------------------
    \begin{lemma}[SNAPG-V2 one step convergence prototype stage-I]\label{lemma:snagp2-one-step-s1-proto}

    \end{lemma}
    \begin{proof}

@@

    \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}
        Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
        Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
        Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
        Then, for all $k \ge 1$, it has the following inequality 
            & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
            - F(\bar x) 
            + \mathbb E_k\left[
                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
            \right]

@@

                    \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
                    - F(\bar x)
                    + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
                + \mathbb E_k\left[
                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
                + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
                \Vert \bar x - v_{k - 1}\Vert^2. 
        And for $k = 0$, it has 
            \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
            + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
            \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 

@@

            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$. 
            \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 

@@

            \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:

@@

                \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
            \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 

@@

>>>>

    \textbf{Notations}. 

@@

        \begin{definition}[smooth Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}

@@

        \begin{theorem}[affine composite smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}

@@

            Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary and, define $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$. 
            Ddenote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$, denote $\Vert A\Vert$ to be the operator norm of the matrix, and $\sigma_{\min}(A)$ to be the smallest non-zero eigenvalues of $A$ in absolute value.
            Then, it satisfies for all $x \in \RR^m, y \in \RR^m$:  
                \frac{\mu \sigma_{\min}(A)^2}{2}\Vert (I - \Pi)(x - y)\Vert^2
                \le \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
                \le D_h(x, y) \le \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$ so it's Semi-SCNVX. 

@@

                &\le \frac{L}{2} \Vert Ax - Ay\Vert^2
                &\le \frac{L\Vert A\Vert^2}{2} \Vert x - y\Vert^2. 
            Using some linear algebra, one can represent $x - y$ as their orthogonal components in $\ker A$, $\ker A^T$ so it has 
                \frac{\mu}{2}\Vert A(x - y)\Vert^2 &= 
                \frac{\mu}{2}\Vert A(\Pi(x - y) + (1 - \Pi)(x - y))\Vert^2
                \frac{\mu}{2}\Vert A(1 - \Pi)(x - y))\Vert^2
                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (1 - \Pi)(x - y)\Vert^2. 
            These results makes for the final inequalities: 
                \frac{\mu\sigma_{\min}(A)}{2}\Vert (I - \Pi)(x - y)\Vert^2
                \le 
                D_h(x, y) \le 
                \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 

@@

        \begin{theorem}[affine minimizer set for aff comp smooth strongly convex]
            \todoinline{NOT FINISHED YET.}

@@

@@

            \begin{assumption}[affine composite Semi-CNVX remative smooth plus non-smooth]\label{ass:snorm-smth-p-nsmth}
                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:aff-smooth-sq-scnvx} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$. 

@@

                    &= F(z) - F(x^+) 

@@

                At (b) we applied results from Theorem \ref{thm:aff-smooth-sq-scnvx}. 
                Continuing it further with the results from \ref{thm:aff-smooth-sq-scnvx} it adds another inequality: 
                    0&\le  F(z) - F(x^+) 

@@

@@

                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
                    &= F(z) - F(x^+) 
                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2
                        + \frac{B}{2}\Vert (I - \Pi)(z - x)\Vert^2
                    &= F(z) - F(x^+) 
                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2

@@

@@

@@

                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2
                    \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu\sigma_{\min}(A)^2}{2}\Vert (I - \Pi) x - y\Vert^2. 
                The second inequality uses Theorem \ref{thm:aff-smooth-sq-scnvx}. 

@@

\section{Stochastic accelerated proximal gradient}
    First, this is an overview of this section.

    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{m\times n}$ matrices and, $b^{(1)}, b^{(2)}, \ldots, b^{(n)}$ be a list of vectors in $\RR^n$. 
        Suppose $F:\RR^m \rightarrow \overline \RR:= \frac{1}{n}\sum_{i = 1}^{n} F_i(x)$, so it admits representations 
        \begin{align*}
            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)}x - b^{(i)}) + g_i(x)
        \end{align*}
        Where, each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $K^{(i)} > \nu^{(i)} \ge 0, b^{(i)} \in \RR^n$ and $A^{(i)} \in \RR^{m \times n}$. 
        So, each $h_i$ are $\nu^{(i)}$ strongly convex and $K^{(i)}$ Lipschitz smooth. 
        \par
        Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$. 
        $f$ satisifes Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
        \begin{align*}
            f(x) = \sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) = h(\mathcal A x). 
        \end{align*}
    \end{assumption}

    \begin{assumption}[sum of many]\label{ass:sum-of-many}
        Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$, so it can be written as: 
        \begin{align*}
            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x)
        \end{align*}
        Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
        \par 
        Take note that, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
    \end{assumption}
    Both assumptions are equivalent, functions satisfies one can be translated in form so it satisfies the other with some extra/fewer parameters. 
    However, it's important to know that for a $F := \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) + g_i(x)$ satisfying Assumption \ref{ass:sum-of-many-aff-comp}, Theorem \ref{thm:pg-ineq-semi-scnvx}, \ref{thm:smnrm-jnsn-smth-nsmth} applies with parameter $\nu^{(i)}\sigma_{\min}(A^{(i)})^2$ for each summees. 
    This can't be known if it only satisfies Assumption \ref{ass:sum-of-many}. 
    \par
    The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
    The following assumption state the interpolation hypothesis in our context. 
    \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
        Suppose that $F := (1/n)\sum_{i = 1}^{n} F_i$ satisfying Assumption \ref{ass:sum-of-many}. 
        In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
        \par
        Consequently, each of the $F_i$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth-x} with $X_i$ being the set of minimizers and, under interpolation hypothesis this equates to non-empty intersections between all $X_i$, i.e: $\bigcap_{i = 1}^n X_i \neq \emptyset$. 
    \end{assumption}

    Due to the fact the algorithms have to be very different support convergence claim for different assumptions on the functions, the following definition gives a generic ideas for all algorithms that specializes on top of it for different assumptions placed on the objective functions. 
    These definitions are not actual algorithms, they are conditions an algorithm must adhere to for the theorems based on it to be valid. 
    Read then as specifications. 
    \begin{definition}[SNAPG-V2 prototype \textcolor{red}{NEW}]\;\label{def:snapg-v2-proto}\\
        Let 
        \begin{enumerate}[nosep]
            \item $F$ satisfies Assumption \ref{ass:sum-of-many}, 
            \item $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$, 
            \item $\sigma^{(k)}$ be another list of i.i.d random variable. 
            \item $\tilde \mu \ge 0$ be a constant that is fixed.
            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 

@@

        The SNAPG prototype specifies algorithm that generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \sigma^{(k)}\right)^{-1}, \\

@@

@@

    \begin{definition}[SNAPG-V2 affine \textcolor{red}{NEW}]\label{def:snapg-v2-aff}
        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
        But in addition, assume that: 
        \begin{enumerate}[nosep]
            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, vectors in $\RR^n$: $(b^{(1)}, \ldots, b^{(n)})$. 
            \item Choose $\sigma^{(k)} = \nu^{(I_k)}\sigma_{\min}(A^{(I_k)})^2$. 
        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters. 
    \begin{definition}[SNAPG-V2 vanilla]\label{def:snapg-v2}
        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
        But in addition, assume that: 
        \begin{enumerate}[nosep]
            \item Choose $\sigma^{(k)} = \mu^{(I_k)}$. 
        Then, SNAPG-V2 vanilla affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters. 

@@

    \begin{lemma}[properties of the iterates on SNAPG-V2 prototype \textcolor{red}{NEW}]\label{lemma:iters-snapg2-proto}
        Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ satisfies Definition \ref{def:snapg-v2-proto}. 

@@

            \item\label{lemma:iters-snapg2-proto-item1} For all $k \ge 1$ it has: 

@@

                    \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
                    + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
            \item\label{lemma:iters-snapg2-proto-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$

@@

        From Definition \ref{def:snapg-v2-proto}:

@@

                1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}}

@@

                \frac{L_k\alpha_k - \sigma^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}}

@@

            = \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}. 

@@

            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} 
                v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}} x_{k - 1}

@@

            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1}
            + \frac{L_k(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1} - y_k
            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}

@@

                \frac{L_k(1 - \alpha_k)}{L_k - \sigma^{(i)}} - (1 - \alpha_k)

@@

            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}

@@

                \frac{L_k - L_k + \sigma^{(i)}}{L_k - \sigma^{(i)}}

@@

            \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}x_{k - 1} - y_k. 

@@

            - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} 
            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}. 

@@

            - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} 
            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})

@@

                \alpha_k - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}

@@

            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})

@@

                \frac{\alpha_kL_k - \alpha_k \sigma^{(i)} - L_k\alpha_k + \sigma^{(i)}}{L_k - \sigma^{(i)}}

@@

            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
            + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}\bar x
            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
            + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).

@@

@@

    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\label{lemma:snagp2-one-step-s1-proto}
        Suppose that the sequence $(y_k, x_k, v_k)$ satisfies Definition \ref{def:snapg-v2-aff}. 
        Fix some $k \in \N, k \ge 1$, suppose that $I_k = i$.
        Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
        Then for all $\bar x \in \RR^m$, the iterates satisfies the inequality: 
            &F_i(x_{k}) - F_i(\bar x) 
            + \frac{L_k\alpha_k^2}{2} \left\Vert \left(I - \Pi^{(i)}\right)(\bar x - v_k)\right\Vert^2

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
                \left\Vert \left(I - \Pi^{(i)}\right)(v_{k - 1} - \bar x)\right\Vert^2
            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
        And when $k = 0$, we have: 
        \todoinline{HERE}

@@

            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{i} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}. 
            \item[(b)] We can use seminorm Jensen's inequality of Theorem \ref{thm:smnrm-jnsn-smth-nsmth} with $z = z_k$ on $F_i$. 

@@

            \item[(d)] Prove in Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item1} we will the equality:

@@

                \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
                + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
            \item [(e)] From Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 

@@

    % The following lemma state the relationships of the iterates generated by SNAPG-V2. 
